\documentclass{article}
%\usepackage{pdflscape}
%\usepackage{afterpage}
%\usepackage{capt-of}
\usepackage{booktabs}
%\usepackage{tabulary}
%\usepackage{rotating}	
%\newcommand{\tabitem}{~~\llap{\textbullet}~~}
\usepackage{longtable}
\usepackage{array} % to call magic m
\usepackage{enumitem} % to remove vertical space for itemize
\usepackage{geometry}
\geometry{a4paper, portrait, margin=1in}
\newcommand{\tabitem}{~~\llap{\textbullet}~~}

\title{Litterature review by topic - burden of health outcomes}
\author{Kenta Okuyama}

\begin{document}
\pagenumbering{gobble}
\maketitle
\tableofcontents
\newpage
\pagenumbering{arabic}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Health outocomes in general
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Burdens of various health outcomes}
\subsection{Physical inactivity}
\begin{itemize}
	\item Physical inactivity is the fourth-leading cause of chronic disease and mortality such as heart disease, stroke, diabetes, and cancers, contributing to over 3 million preventable deaths annually worldwide (WHO. Global recommendations on physical activity for health. Geneva. WHO; 2010. p. 58.)
	\item 60\% of adult population in the world does not reach the recommended level of physical activity (WHO. The World health report:2002:Reducing the riss, promoting healthy life. Geneva. WHO; 2002. p.248.)
	\item Physical inactivity is the fifth leading risk facto for burden of disease for women in Sweden and the sixth leading risk factor for men (Agardh E, Moradi T, Allebeck P. The contribution of risk factors to the burden of disease in Sweden. A comparison between Swedish and wHO data. Lakartidningen. 2008.)
	\item Exercise is defined as "planned, structured, and repetitive and purposive in the sense that the improvement or maintenance of one or more components of physical fitness is the objective", subcategory of physical activity (Physical Activity Guidelines Advisory Committee. Physical Activity Guidelines Advisory Committee Report, 2008.)
\end{itemize}

\subsection{Mental illness}
\begin{itemize}
	\item Mental illness including anxiety is oone of the leading causes of disability worldwide (WHO. The World Health report 2001. Mental health, new understanding, new hope. Geneva: 2001; Murracy CJ, Lopez AD. Global mortality, disability, and the contribution of risk factors: Global Burden of Disease Study. Lancet. 1997;349:1436-42.)
\end{itemize}

\subsection{Pain}
\begin{itemize}
	\item 
\end{itemize}








\end{document}
